---
title: Krvaven data
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    number_sections: no
    toc: yes
---
  
******



```{r setup, include = F}

# load packages
library(knitr)
library(rmarkdown)
library(tidyverse)
library(tabulizer)
library(janitor)
library(here)
library(broom)
opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F, cache = F)

make_corr_plot <- function(current_df){
  
  ALPHA <- .05
  cols <- rev(colorRampPalette(c("red", "white", "blue"))(100))
  
  clean_df <- current_df %>%
    select_if(is.numeric) 
  
  corr_mat <- cor(clean_df, 
                  use = "pairwise.complete.obs")
  
  p.mat <- corrplot::cor.mtest(clean_df, 
                               conf.level = (1-ALPHA),  
                               use = "pairwise.complete.obs")$p
  
  corrplot::corrplot(corr_mat, method = "color",  col = cols,
                     order = "original", number.cex = .7,
                     addCoef.col = "black", 
                     p.mat = p.mat, sig.level = ALPHA, insig = "blank", 
                     tl.col = "black", tl.srt = 90,
                     diag = FALSE)
  
}

tidy_r_to_text_r <- function(tidy_row){
  round_tidy <- tidy_row %>%
    mutate_at(vars(estimate, contains("conf")), round, 2)
  
  p_value <- case_when(pull(round_tidy, p.value) < .0001 ~ "_p_ < .0001",
                       pull(round_tidy, p.value) < .001 ~ "_p_ < .001",
                    #   pull(round_tidy, p.value) < .01 ~ "_p_ < .01",
                       TRUE ~ paste0("_p_ = ", round(pull(round_tidy, p.value),3)))
  
  paste0(
    "_r_(",
    pull(round_tidy, parameter),
    ") = ", 
    pull(round_tidy, estimate),
    " [",
    pull(round_tidy, conf.low),
    ", ",
    pull(round_tidy, conf.high),
    "], ",
    p_value
  )
}
```


```{r}
TIDY_DATA_PATH <- here("data/analysis_1/tidy_kvarven.csv")
tidy_data<- read_csv(TIDY_DATA_PATH)

wide_df_full <- tidy_data %>%
  select(table_name, id, n, es) %>%
  pivot_wider(names_from = "table_name", values_from = c(n, es)) %>% 
  select(id, es_original_studies, es_replication_studies, es_RE_MA,
         "es_PET-PEESE_MA", es_PSM_MA, es_TF_MA)  %>%
  left_join(tidy_data %>% filter(table_name == "original_MA") %>%
              select(id, tau)) %>%
  mutate(tau2 = tau,
         tau = sqrt(tau2),
         log_tau2 = log(tau2 + .0001))

```

## Pairwise correlations{.tabset}
### All MAs
```{r}
wide_df_full %>%
  select(-id) %>%
  make_corr_plot()
```

Some evidence that a replication effect size is bigger when the corresponding meta-analysis is hetergeneous.

### Excluding Srull & Wyer (1979)
One effect - Srull & Wyer (1979) - has a massive original effect size (~3) that strongly influences the magnitude of the correlations with the original es. Here's what the correlations look like when you exclude this point. 
```{r}
wide_df_full %>%
  filter(id != 14) %>%
  select(-id) %>%
  make_corr_plot()
```



## Pairwise plots
```{r}
# wide df of original, ma, and replication with n and es, and cis for es
wide_df <- tidy_data %>%
  select(table_name, id, n, es) %>%
  pivot_wider(names_from = "table_name", 
              values_from = c(n, es)) %>%
  mutate(n_RE_MA = n_original_MA) %>%
  select(id, n_replication_studies, n_original_studies, n_RE_MA,
         es_replication_studies, es_original_studies, es_RE_MA, es_original_MA) %>%
  left_join(tidy_data %>% filter(table_name == "replication_studies") %>%
              select(id, ci_lower, ci_upper)) %>%
  rename(ci_lower_es_replication = ci_lower,
         ci_upper_es_replication = ci_upper) %>%
  left_join(tidy_data %>% filter(table_name == "RE_MA") %>%
              select(id, ci_lower, ci_upper)) %>%
  rename(ci_lower_es_RE_MA = ci_lower,
         ci_upper_es_RE_MA = ci_upper) %>%
  left_join(tidy_data %>% filter(table_name == "original_studies") %>%
              select(id, ci_lower, ci_upper)) %>%
  rename(ci_lower_es_original_study = ci_lower,
         ci_upper_es_original_study = ci_upper) %>%
  left_join(tidy_data %>% filter(table_name == "original_MA") %>%
              select(id, tau)) %>%
  mutate(tau2 = tau, 
         tau = sqrt(tau2),
         log_tau2 = log(tau2 + .0001))
```

### All MAs{.tabset}
#### Replication vs. MA (RE)
```{r}
rep_ma <- cor.test(wide_df$es_RE_MA, 
                   wide_df$es_replication_studies)

paper_fig <- ggplot(wide_df, aes(y = es_replication_studies,
                    x = es_RE_MA)) +
  geom_errorbarh(aes(xmin = ci_lower_es_RE_MA, 
                     xmax = ci_upper_es_RE_MA, height = 0)) +
  geom_linerange(aes(ymin = ci_lower_es_replication, 
                      ymax = ci_upper_es_replication))+
  geom_point(size = 1.5) +
  #  geom_point( aes(size = log(n_RE_MA))) +

  #geom_label(aes(label = id) )+
  geom_abline(intercept = 0, slope = 1, linetype = 2) +
  #ggtitle("Re-Analysis of Kvarven et al.") +
  geom_smooth(method = "lm", alpha = .1) +
  ylim(-.3, 1.2) +
   annotate("text", x = .9, y = -.15, 
           label = paste0("italic(r)==", round(rep_ma$estimate,2)), 
           size = 4, color = "red", parse = T) +
  ylab("Multi-Lab Replication Effect Size") +
  xlab("Meta-Analytic Effect Size") +
  theme(axis.line = element_line(size = .8)) +

  theme_classic(base_size = 12)
paper_fig

cor_to_print <- tidy_r_to_text_r(tidy(rep_ma))
```



```{r, eval = F}
pdf(file = here("results/analysis_1/fig1a.pdf"), width = 4, height = 4)
paper_fig
dev.off()
```



`r cor_to_print`


Compare to correlation with original MA efect size:
```{r}

rep_ma_orig <- cor.test(wide_df$es_original_MA, 
                   wide_df$es_replication_studies)

cor_to_print_orig <- tidy_r_to_text_r(tidy(rep_ma_orig))
```

`r cor_to_print_orig`

#### Replication vs. Original
```{r}
original_ma <- cor.test(wide_df$es_original_studies,
                        wide_df$es_replication_studies)

wide_df %>%
  ggplot( aes(y = es_replication_studies,
                    x = es_original_studies)) +
  geom_pointrange(aes(ymin = ci_lower_es_replication, 
                      ymax = ci_upper_es_replication)) +
  geom_errorbarh(aes(xmin = ci_lower_es_original_study, 
                     xmax = ci_upper_es_original_study, height = 0)) +
  geom_abline(intercept = 0, slope = 1, linetype = 2) +
  ylim(-.3, 1.2) +
  ggtitle("Re-Analysis of Kvarven et al.") +
  geom_smooth(method = "lm", alpha = .2) +
  annotate("text", x = .9, y = -.1, 
           label = paste0("italic(r) ==", round(original_ma$estimate,2)), 
           size = 8, color = "red", parse = T) +  
  ylab("Multi-Lab Replication Effect Size") +
  xlab("Original Study Effect Size") +
  theme_classic(base_size = 15)
```

### Excluding Srull & Wyer (1979){.tabset}
```{r}
wide_df_excl <- wide_df %>%
  filter(id != 14)
```

#### Replication vs. MA (RE)
```{r}
rep_ma_excl <- cor.test(wide_df_excl$es_RE_MA, wide_df_excl$es_replication_studies)  

ggplot(wide_df_excl, aes(y = es_replication_studies,
                    x = es_RE_MA)) +
  geom_errorbarh(aes(xmin = ci_lower_es_RE_MA, 
                     xmax = ci_upper_es_RE_MA, height = 0)) +
  geom_pointrange(aes(ymin = ci_lower_es_replication, 
                      ymax = ci_upper_es_replication))+
  geom_abline(intercept = 0, slope = 1, linetype = 2) +
  ggtitle("Re-Analysis of Kvarven et al.") +
  geom_smooth(method = "lm", alpha = .2) +
  ylim(-.3, 1.2) +
  annotate("text", x = .9, y = -.1, 
           label = paste0("r = ", round(rep_ma_excl$estimate,2)), 
           size = 8, color = "red") +
  ylab("Multi-Lab Replication Effect Size") +
  xlab("Meta-Analytic Random Effect Effect Size") +
  theme_classic(base_size = 15)


```

```{r}
cor_to_print_exclude<- tidy_r_to_text_r(tidy(rep_ma_excl))
```

`r cor_to_print_exclude`


#### Replication vs. Original
```{r}
original_ma_excl <- cor.test(wide_df_excl$es_original_studies,          wide_df_excl$es_replication_studies)

wide_df_excl %>%
  ggplot( aes(y = es_replication_studies,
                    x = es_original_studies)) +
  geom_pointrange(aes(ymin = ci_lower_es_replication, 
                      ymax = ci_upper_es_replication)) +
  geom_errorbarh(aes(xmin = ci_lower_es_original_study, 
                     xmax = ci_upper_es_original_study, height = 0)) +
  geom_abline(intercept = 0, slope = 1, linetype = 2) +
  ggtitle("Re-Analysis of Kvarven et al.") +
  geom_smooth(method = "lm", alpha = .2) +
  ylim(-.3, 1.2) +
  annotate("text", x = .9, y = -.1, 
           label = paste0("r = ", round(original_ma_excl$estimate,2)), 
           size = 8, color = "red") +  
  ylab("Multi-Lab Replication Effect Size") +
  xlab("Original Study Effect Size") +
  theme_classic(base_size = 15)
```

### Tau2 vs. replication effect size

```{r}
wide_df %>%
  ggplot( aes(y = es_replication_studies,
                    x = tau2)) +
  geom_pointrange(aes(ymin = ci_lower_es_replication, 
                      ymax = ci_upper_es_replication)) +
  ggtitle("Re-Analysis of Kvarven et al.") +
  geom_smooth(method = "lm", alpha = .2) +
  ylab("Multi-Lab Replication Effect Size") +
  xlab("log Tau2") +
  theme_classic(base_size = 15)
```

## ES Differences Plots{.tabset}
Comparing replication minus MA estimate vs. replicaiton minus original estimate. Note: this is just the simple difference, but we probably want a model that takes into account the sample sizes for each effect. I think they did some version of this in the paper, but I can't figure out what they did.

### All 
```{r}
es_diffs <- wide_df %>%
  select(id, contains("es_"), contains("tau"),
         -contains("ci")) %>%
  mutate(abs_dif_original = abs(es_replication_studies - es_original_studies),
         abs_dif_ma = abs(es_replication_studies - es_RE_MA),
         dif_original = es_replication_studies - es_original_studies,
         dif_ma = es_replication_studies - es_RE_MA) %>%
  select(id, contains("dif"), contains("tau"))
```

```{r}
es_diffs %>%
  select(-id) %>%
  make_corr_plot()
```

```{r}
es_diffs_long <- es_diffs %>%
    pivot_longer(-id, names_to = "measure", 
                 values_to = "es_dif") %>%
    filter(!(measure %in% c("tau", "log_tau2", "tau2",
                            "abs_dif_ma",
                            "abs_dif_original")))

mean_diffs <- es_diffs_long %>%
  group_by(measure) %>%
  summarize(mean  = mean(es_dif),
            sd  = sd(es_dif),
            n = n(),
            ci_95_range = 1.96  * sd/sqrt(n),
            ci_lower = mean - ci_95_range,
            ci_upper = mean + ci_95_range) %>%
  mutate(y = c(2.5, 2.4))

ggplot(es_diffs_long)  +
  geom_density(aes(fill = measure, x = es_dif), alpha = .5) +
  geom_point(data = mean_diffs, aes(x = mean, y = y, 
                                    color = measure), 
             size = 3) +
  geom_errorbarh(data = mean_diffs, 
                 aes(xmin = ci_lower, xmax = ci_upper, 
                     color = measure, y = y), 
                 height = 0, size = 1) +
  xlab("Difference from Replication Estimate") +
  theme_classic(base_size = 15)
```

### Excluding Srull & Wyer (1979)
```{r}
es_diffs_excl <- wide_df_excl %>%
  select(id, contains("es_"), contains("tau"),
         -contains("ci")) %>%
  mutate(abs_dif_original = abs(es_replication_studies - es_original_studies),
         abs_dif_ma = abs(es_replication_studies - es_RE_MA),
         dif_original = es_replication_studies - es_original_studies,
         dif_ma = es_replication_studies - es_RE_MA) %>%
  select(id, contains("dif"), contains("tau")) 
```

```{r}
es_diffs_excl %>%
  select(-id) %>%
  make_corr_plot()
```


```{r}
es_diffs_excl_long <- es_diffs_excl %>%
  pivot_longer(-id, names_to = "measure", 
               values_to = "es_dif")  %>%
  filter(!(measure %in% c("tau", "log_tau2", "tau2",
                          "abs_dif_ma", "abs_dif_original")))

mean_diffs_excl <- es_diffs_excl_long %>%
  group_by(measure) %>%
  summarize(mean  = mean(es_dif),
            sd  = sd(es_dif),
            n = n(),
            ci_95_range = 1.96  * sd/sqrt(n),
            ci_lower = mean - ci_95_range,
            ci_upper = mean + ci_95_range) %>%
  mutate(y = c(2.5, 2.4))

ggplot(es_diffs_excl_long)  +
  geom_density(aes(fill = measure, x = es_dif), alpha = .5) +
  geom_point(data = mean_diffs_excl, aes(x = mean, y = y, 
                                         color = measure), 
             size = 3) +
  geom_errorbarh(data = mean_diffs_excl, 
                 aes(xmin = ci_lower, xmax = ci_upper, 
                     color = measure, y = y), height = 0, size = 1) +
  xlab("Difference from Replication Estimate") +
  theme_classic(base_size = 15)
```

# Models{.tabset}
## All ES

```{r}
lm(es_replication_studies ~ es_RE_MA, data = wide_df) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_original_studies, data = wide_df) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ tau2, data = wide_df) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_RE_MA + es_original_studies, 
   data = wide_df) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_RE_MA + tau2, 
   data = wide_df) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_RE_MA + tau2, 
   data = wide_df) %>%
  summary()
```



```{r}
lm(es_replication_studies ~ es_RE_MA + es_original_studies + tau2, 
   data = wide_df) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_RE_MA + es_original_studies + tau2, 
   data = wide_df, weights = log(n_original_studies)) %>%
  summary()
```


## Excluding Excluding Srull & Wyer (1979)
```{r}
lm(es_replication_studies ~ es_RE_MA, data = wide_df_excl) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_original_studies, data = wide_df_excl) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ tau2, data = wide_df_excl) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_RE_MA + es_original_studies, 
   data = wide_df_excl) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_RE_MA + tau2, 
   data = wide_df_excl) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_RE_MA + es_original_studies + tau2, 
   data = wide_df_excl) %>%
  summary()
```

```{r}
lm(es_replication_studies ~ es_RE_MA + es_original_studies + tau2, 
   data = wide_df_excl, weights = log(n_original_studies)) %>%
  summary()
```

